\chapter{Anhang B: Quellenverzeichnis und Bibliografie}
Nachfolgend sind die in der Arbeit zitierten Quellen und die für die Recherche 
verwendete Bibliografie verzeichnet.

\clearpage

\section*{Quellenverzeichnis}

\subsection*{Paper: A Study of MAC Address Randomization.}
\begin{itemize}
    \item Name: Study of MAC Address Randomization in Mobile Devices and 
    When it Fails
    \item Autoren: Jeremy Martin, Travis Mayberry, Collin Donahue et al.
    \item Publikation: 2017, Proceedings on Privacy Enhancing Technologies 
\end{itemize}

\subsection*{Paper: Defeating MAC Address Randomization Through Timing Attacks}
\begin{itemize}
    \item Name: Defeating MAC Address Randomization Through Timing Attacks
    \item Autoren: Célestin Matte, Mathieu Cunche, Franck Rousseau et al.
    \item Publikation: 2016, WiSec Ausgabe Juli 2016
\end{itemize}

\subsection*{Paper: How Talkative is Your Mobile Device?}
\begin{itemize}
    \item Name: How Talkative is your Mobile Device? An Experimental Study of Wi-Fi 
    Probe-Requests
    \item Autoren: Julien Freudinger
    \item Publikation: 2015, WiSec Ausgabe Juni 2015
\end{itemize}

\subsection*{Paper: Noncooperative 802.11 MAC Layer Fingerprinting}
\begin{itemize}
    \item Name: Noncooperative 802.11 MAC Layer Fingerprinting and Tracking
    of Mobile Devices
    \item Autoren: Pieter Robyns, Bram Bonné, Peter Quax and Wim Lamotte
    \item Publikation: 2017, Hindawi Security and Communication Networks Volume 2017
\end{itemize}

\subsection*{Paper:Why MAC Address Randomization is not Enough}
\begin{itemize}
    \item Name: Why MAC Address Randomization is not Enough: 
    An Analysis of Wi-Fi Network Discovery Mechanisms
    \item Autoren: Mathy Vanhoef, Célestin Matte, Mathieu Cunche et al.
    \item Publikation: 2016, ASIA CSS Ausgabe 2016
\end{itemize}

\subsection*{Pyshark - Packet parser using wireshark's tshark}
\begin{itemize}
    \item Name: Pyshark Dokumentation
    \item Maintainer: KimiNewt
    \item URL \url{https://kiminewt.github.io/pyshark/}
\end{itemize}

\subsection*{Scapy}
\begin{itemize}
    \item Name: Scapy Dokumentation
    \item Autoren: Biondi Philippe
    \item URL: \url{https://scapy.readthedocs.io/en/latest/introduction.html}
\end{itemize}

\clearpage

\section*{Bibliografie}
 
Apple Inc. Use private Wi-Fi addresses in iOS 14, iPadOS 14, and \\ watchOS 7 \\
\url{https://support.apple.com/en-us/HT211227} \\
Abgerufen am 23.09.2020 \\
\newline
Apple Inc. iOS 14 Per-Network MAC Addresses \\
\url{https://developer.apple.com/forums/thread/651151} \\
Abgerufen am 23.09.2020 \\
\newline
Buberenko Volodymyr. Diving into Android Oreo security changes. \\
\url{https://uptech.team/blog/android-oreo-security-changes} \\
Abgerufen am 25.09.2020 \\
\newline
Buberenko Volodymyr. Android Oreo: all you need to know. \\
\url{https://uptech.team/blog/android-oreo-overview} \\
Abgerufen am 25.09.2020 \\
\newline
Cisco. Fundamentals of 802.11 Wireless Sniffing. \\
\url{https://www.cisco.com/c/en/us/support/docs/wireless-mobility/80211/200527-Fundamentals-of-802-11-Wireless-Sniffing.html} \\
Abgerufen am 03.10.2020 \\
\newline
David (Nachname Unbekannt). How to handle randomized MAC addresses on Android 9+ and iOS 14+. \\
\url{https://support.adamnet.works/t/how-to-handle-randomized-mac-addresses-on-android-9-and-ios-14/316} \\
Abgerufen am 29.09.2020 \\
\newline
Dorsey Brannon. The Perils of Probe Requests. \\
\url{https://medium.com/@brannondorsey/wi-fi-is-broken-3f6054210fa5} \\
Abgerufen am 30.09.2020 \\
\newline
Edwards Jim. Apple's New Anti-Tracking System For iPhones Doesn't Work, Researcher Claims.
\url{https://www.businessinsider.com/ios-8-mac-randomization-wifi-iphone-doesnt-work-2014-10} \\
Abgerufen am 22.09.2020 \\  
\clearpage 
Gast, Mathew S. 802.11 Wireless Networks: Chapter 4, 802.11 Framing in Detail.
Oreilly: \url{https://www.oreilly.com/library/view/80211-wireless-networks/0596100523/ch04.html} \\
\newline
Gast, Mathew S. 802.11 Wireless Networks: The Definitive Guide, 2nd Edition.
Oreilly: \url{https://www.oreilly.com/library/view/80211-wireless-networks/0596100523/} \\
\newline
Goodin Dan. Shielding MAC addresses from stalkers is hard and Android fails miserably at it.
\url{https://arstechnica.com/information-technology/2017/03/shielding-mac-addresses-from-stalkers-is-hard-android-is-failing-miserably/} \\
Abgerufen am 22.09.2020 \\ 
\newline
Google LLC. Privacy: MAC Randomization. \\
\url{https://source.android.com/devices/tech/connect/wifi-mac-randomization} \\
Abgerufen am 23.09.2020 \\ 
\newline
Google LLC. Android Enterprise Security White Paper. \\
\url{https://static.googleusercontent.com/media/www.android.com/de//static/2016/pdfs/enterprise/Android_Enterprise_Security_White_Paper_2019.pdf} \\
Abgerufen am 23.09.2020 \\
\newline
Harris Nik . Tracking People \& Devices with WiFi. \\
\url{https://nikharris.com/tracking-people/} \\
Abgerufen am 20.11.2020 \\
\newline
Hetting Claus. New ‘Private Address’ iPhone feature could severely impact the Wi-Fi industry, expert says.
\url{https://wifinowglobal.com/news-and-blog/new-private-wi-fi-address-iphone-feature-could-severely-impact-the-wi-fi-industry-expert-says/}\\
Abgerufen am 22.09.2020 \\
\newline
Jankie Michael. We analyse WWDC19. iOS 13 cracks down on location tracking.
\url{https://whatthe.fi/we-analyse-wwdc19-ios-13-cracks-down-on-location-tracking-4a4167b0d7d5} \\
Abgerufen am 23.09.2020 \\
\newline
Johannes (Nachname Unbekannt). MAC Address Randomization on iOS.
\url{https://www.turais.de/mac-address-randomization-on-ios-12/} \\
Abgerufen am 23.09.2020 \\
\clearpage 
Mamiit Aaron. Apple implements random MAC address on iOS 8. Goodbye, marketers.
\url{https://www.techtimes.com/articles/8233/20140612/apple-implements-random-mac-address-on-ios-8-goodbye-marketers.htm} \\
Abgerufen am 23.09.2020 \\
\newline
Nayanajith Rasika. CWAP 802.11- Probe Request/Response. \\
\url{https://mrncciew.com/2014/10/27/cwap-802-11-probe-requestresponse/} \\
Abgerufen am 10.10.2020 \\
\newline
Peterson Mike. iOS 14 MAC randomization privacy feature may cause Cisco enterprise network issues. \\
\url{https://appleinsider.com/articles/20/09/17/ios-14-mac-randomization-privacy-feature-may-cause-cisco-enterprise-network-issues} \\
Abgerufen am 01.10.2020 \\
\newline
Wikipedia. IEEE 802.11 - Channels and frequencies. \\
\url{https://en.wikipedia.org/wiki/IEEE_802.11#Channels_and_frequencies} \\
Abgerufen am 03.10.2020 \\
